Data integration

### 2010-04-27 docs/DataIntegration/DataIntegration.tex
This is for a specific target conference. SO, put it here separately.Later on, we can move it to other part.

select record\_id from data\q_tables
where condition column 1='value1' and (context column1 = 'context
value' or context column2 = `context value', etc.);

>>>>

select record\_id from data\_tables
where condition column 1='value1' and (context column1 = 'context
value' or context column2 = `context value', etc.);
